---
title: "Regression Analysis"
author: "Hailey Hartman"
format: docx
editor: visual
---

# IMPORTANT INFO

This document is built with placeholders for your companies ticker, **you are responsible for finding each instance and replacing**. If your code is giving you an error indicating that "xxxx object is not found" and the object is referencing a ticker that is not yours you have missed a place you need to replace.

From here out you will be able to create professional graphs and analysis.

# Loading Data and Libraries

```{r,results="hide",warning=FALSE, message=FALSE}

library(quantmod)
library(tidyquant)
library(dplyr)
library(tidyr)
library(sandwich)
library(lmtest)

```

# Company vs One Indicator

#### Loading Company Name

Times to replace with ticker: 5

Times to replace with indicator: 0

```{r}

# 1. Get stock prices and compute returns
HIW_prices <- tq_get("HIW", get = "stock.prices", from = "2025-01-01")
HIW_returns <- HIW_prices |>
  tq_transmute(select     = adjusted,
               mutate_fun = periodReturn,
               period     = "daily",
               type       = "log",
               col_rename = "HIW")


```

#### Loading and Cleaning Indicator

Times to replace with ticker: 0

Times to replace with indicator: 3

```{r}
# 2. Get Indicator 
Indicator_data <- tq_get("CPIAUCSL", get = "economic.data", from = "2025-01-01")

# 3. Forward-fill GDP to daily frequency
Indicator_daily <- Indicator_data |>
  dplyr::rename(CPIAUCSL = price) |>   
  tidyr::complete(date = seq.Date(min(date), max(date), by = "day")) |>
  tidyr::fill(CPIAUCSL)
```

#### Creating Merged Data set

Times to replace with ticker: 1

Times to replace with indicator: 0

```{r}
# 4. Merge stock returns with GDP
merge <- HIW_returns |>
  left_join(Indicator_daily, by = "date")
head(merge)
```

#### Creating Regression Output

Times to replace with ticker: 1

Times to replace with indicator: 1

```{r}
# 5.  Estimate the model.
model<- lm(HIW ~ CPIAUCSL, data = merge) 

#6.  Apply Newey-West standard Error to get final model
nw_se <- NeweyWest(model, lag= 5, prewhite= F)
coeftest(model, vcov. = nw_se)
```

## Follow Up Analysis for One Indicator Model

#### Plotting Residuals

Times to replace with ticker: 0

Times to replace with indicator: 0

```{r}
library(ggplot2)
library(broom)
library(scales)
library(tseries)
# 1. Create Simple regression (CCI ~ FEDFUNDS)

simple_nw5 <- NeweyWest(model, lag = 5)

# 1. Merge and clean data

aug_simple <- augment(model, newdata = merge)
stopifnot(nrow(merge) == nrow(aug_simple))    

merge <- merge %>%
  mutate(
    resid_simple  = aug_simple$.resid,
    fitted_simple = aug_simple$.fitted)

# 2. Plot: residuals over time 
p_resid_time <- ggplot(merge, aes(x = date, y = resid_simple)) +
  geom_line(color = "steelblue", na.rm = TRUE) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(title = "Residuals over time ", x = "Date", y = "Residual")

print(p_resid_time)
```

# Company vs Fama-French Factors (Cahart 4-Factor Model)

#### Getting Fama-French daily Factor Data

**REMINDER:** This data has to be downloaded to your computer and stored in the same folder that R is running out of. If you are having issues loading CSV search "R programming csv reading issues" in your preferred search engine – I do **not** recommend using OpenAI.

Times to replace with ticker: 0

Times to replace with indicator: 0

```{r}
# 1.  Load Fama-French data

library(tidyverse)
ff3 <- read_csv("F-F_Research_Data_Factors_daily.csv")
ff_mom <- read_csv("Developed_MOM_Factor_Daily.csv")

# 2.  Clean Data 

ff3 <- ff3 %>%
  mutate(date = as.Date(as.character(date), format = "%Y%m%d"))
ff3 <- ff3 %>%
  mutate(across(-date, ~ .x / 100))

ff_mom <- ff_mom %>%
  mutate(date = as.Date(as.character(date), format = "%Y%m%d"))
ff_mom <- ff_mom %>%
  mutate(across(-date, ~ .x / 100))

```

#### Creating Merged Data set

Times to replace with ticker: 1

Times to replace with indicator: 0

```{r}
# 3.  Merging Fama-French Data with the stock of your choice
merged_ff3_data <- HIW_returns %>%
  left_join(ff3, by = "date") %>%
  left_join(ff_mom, by = "date")
```

#### Creating Regression Output

Times to replace with ticker: 1

Times to replace with indicator: 0

```{r}
# 4. Estimate the Cahart model
carhart_model <- lm((HIW - RF) ~ `Mkt-RF` + SMB + HML + WML, data = merged_ff3_data)


# 5.  function to get coeftest with Newey-West at chosen lag and robust CIs
nw_report <- function(lm_obj, lag = 5, conf_level = 0.95) {
  vcov_nw <- NeweyWest(lm_obj, lag = lag, prewhite = FALSE)
  ct <- coeftest(lm_obj, vcov. = vcov_nw)          # table with est, se, t, p
  ests <- coef(lm_obj)
  ses <- sqrt(diag(vcov_nw))
  alpha <- (1 - conf_level) / 2
  z <- qnorm(1 - alpha)
  cis <- cbind(ests - z * ses, ests + z * ses)
  res <- broom::tidy(lm_obj) %>%
    mutate(nw_se = ses, nw_lwr = cis[,1], nw_upr = cis[,2]) %>%
    select(term, estimate, nw_se, nw_lwr, nw_upr) 
  list(coeftest = ct, tidy = res, vcov_nw = vcov_nw)}

carhart_nw5 <- nw_report(carhart_model, lag = 5)

# 6. print human-friendly tables
carhart_nw5$tidy
coeftest(carhart_model, vcov. = nw_se)



```

## Follow Up Analysis for Carhart Model

#### Visualizing Confidence Intervals

Times to replace with ticker: 0

Times to replace with indicator: 0

```{r}
# 1. prepare tidy table for carhart_model with NW(5)
car_tidy <- carhart_nw5$tidy

# 2. Create Plot
ggplot(car_tidy %>% filter(term != "(Intercept)"),
       aes(x = term, y = estimate)) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = nw_lwr, ymax = nw_upr), width = 0.2) +
  coord_flip() +
  labs(title = "Carhart factor loadings with Newey-West (lag=5) 95% CIs",
       x = "Factor", y = "Estimate")

```

#### Visualizing Cumulative Abnormal Returns

Times to replace with ticker: 0

Times to replace with indicator: 0

```{r}
library(broom)
library(dplyr)
library(ggplot2)
library(scales)
library(tidyr)

# 1.Creat augment aligned residuals/fitted
aug <- augment(carhart_model, newdata = merged_ff3_data)

# 2. Stop check at common error
stopifnot(nrow(merged_ff3_data) == nrow(aug))

# 3. Clean and merge data
merged_ff3_data <- merged_ff3_data %>%
  mutate(
    resid_carhart  = aug$.resid,
    fitted_carhart = aug$.fitted)

N <- nrow(merged_ff3_data)
intercept_alpha <- coef(carhart_model)["(Intercept)"]

merged_ff3_data <- merged_ff3_data %>%
  arrange(date) %>%
  mutate(
    resid_for_cumsum = replace_na(resid_carhart, 0),
    CAR = cumsum(resid_for_cumsum),
    CAR_alpha = cumsum(rep(intercept_alpha, N))
  )

# 4. Create plot
ggplot(merged_ff3_data, aes(x = date)) +
  geom_line(aes(y = CAR), color = "firebrick", na.rm = TRUE) +
  labs(title = "Cumulative Abnormal Returns ", y = "Cumulative return", x = "Date") +
  scale_y_continuous(labels = percent_format(accuracy = 0.01))
```

#### Testing Various Lags

Times to replace with ticker: 0

Times to replace with indicator: 0

```{r}

lags <- c(0, 3, 5, 10, 20)
robust_lag_table <- map_df(lags, function(L) {
  vc <- NeweyWest(carhart_model, lag = L, prewhite = FALSE)
  se <- sqrt(diag(vc))
  est <- coef(carhart_model)
  tibble(lag = L,
         term = names(est),
         estimate = as.numeric(est),
         nw_se = as.numeric(se),
         t_stat = estimate / nw_se,
         p_val = 2 * pnorm(-abs(t_stat)))
})
robust_lag_table %>% pivot_wider(names_from = term, values_from = c(estimate, nw_se, t_stat, p_val))
```
